Binning Strategies and Related Loss for Large Data

### 2016-12-05 AuthorResponseToReviewers.Rmd

- The main result from the paper is to provide simple adjustment recommendations for binning specification for reducing loss in binned scatterplots. To emphasize these recommendations, the baseball plot example in Section 5.3 has been reworked to highlight the take-home message. To your other point, we agree that future work to quantify the implicit loss of information (e.g. the imprecise ability to map continuously shaded tiles to a frequency legend) in reading binned scatterplots is needed; however, the current work strives to quantify explicit loss of information when the perception tasks are more simple (e.g. mapping distinguishably-discrete shaded tiles to an interval on the frequency legend).

### Responses to Editors Comments/Questions
*Editor's Comments to Author:*

*Associate Editor - Comments to the Author:*
*The paper in its current form does not provide a sufficiently thorough coverage of either review material or novel material to warrant publication.  However, the reviewers have some useful suggestions for ways in which a different paper (or two) could possibly be produced by expanding on different parts of this submission.*

- We hope that the revisions expanding review material and clarification of our contributions to the topic will meet the standards of your publication. An R-package with binning, loss and plotting functions is available through an author's Github repository; however linking directly would not allow for blinded review. As such the functions used are provided in a supplementary R file labeled "BinPackageFunctions.R".  Additionally, a link to the R package on Github can be provided to the editor(s) upon request. If there are any additional comments, concerns or questions, our team is happy to address them.
